On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-07-31 paper/paper.tex
Fix citation to correct work

Additionally, lambdas can also be difficult to implement in EDSLs. A major reason
for this is that control flow constructs which are typically \textit{outside} the EDSL,
such as pattern matching and tail recursion, can make it challenging to "look inside"
the lambda. When these control structures are reified within the EDSL, it is
easier to also reify lambdas using the dummy argument technique described in~\cite{Gill:2014:DSLSynth}.

>>>>

Additionally, lambdas can also be difficult to implement in EDSLs. A major reason
for this is that control flow constructs which are typically \textit{outside} the EDSL,
such as pattern matching and tail recursion, can make it challenging to "look inside"
the lambda. When these control structures are reified within the EDSL, it is
easier to also reify lambdas using the dummy argument technique described in~\cite{Elliott:03:CompileDSEL-JFP}.
